### 2018-02-08 Paper/jaccardbaetica.tex
update paper

We analysed a dataset of 990 stamps from 81 workshops. From the dataset, a sample of 131 different stamps were identified and collected from from CEIPAC database (citar). The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance. The chronology in the workshops is widely diverse from I-III B.C. However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason can be that most of them were partially excavated focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

Considering our dataset as non-uniform sample, this method provides a useful tool to handle large samples with different sizes and diversity. Morisita-Horn index can be expressed considering 0 as total presence of similarity of stamps and 1 a totally dissimilarity between stamps.

@@

@@

The research was funded by European Research Council Advanced Grant
EPNet (340828).

>>>>

\subsection{Case study}

Our case study ....
We analysed a dataset of 990 stamps from 81 workshops. A sample of 131 different stamps were identified and collected from CEIPAC database (citar). The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance. The chronology in the workshops is widely diverse from I-III B.C. However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason can be that most of them were partially excavated focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

Considering our dataset as non-uniform sample, this method provides a useful tool to handle large samples with different sizes and diversity \citep{wolda_similarity_1981}. Morisita-Horn index can be expressed considering 0 as total presence of similarity of stamps and 1 a totally dissimilarity between stamps.

@@

There is not connection between stamps and amphora workshops

There is not similar stamps in closest workshop

Similar stamps were not found in closest amphorae workshops so it could be interpreted as no direct connection between stamps and the location of amphora workshops were found.

@@

The research was funded by European Research Council Advanced Grant
EPNet (340828). We are grateful to 
All data has been analysed and conducted in R program version 3.2.4, using vegan package (citar)
